Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-07 Tex/Paper.tex
Daily commit

@@

\subsection[\label{S:M:Setup}]{Simulation Setup}

In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
see from the self-modulated SPS beam. This was done both to reduce simulation time, as we run 3D simulations, and to
create a stable environment for the witness beam.

@@

%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
%~   unloaded wake)
The structure of the single drive beam set-up behaves similarly to the self-modulated case. However, since the drive
beam is prevented from significant evolution in this simulation set-up, we are presented with an idealised case where
the electron witness beam sees consistent fields.

>>>>

% Custom Commands
%*****************

% Text
%~ \newcommand{\eq}[1]{Eq. \ref{#1}}
%~ \newcommand{\fig}[1]{Fig. \ref{#1}}
%~ \newcommand{\tbl}[1]{Table \ref{#1}}

% Math
\newcommand{\unit}[1]{\,\mathrm{#1}}
\newcommand{\funit}[2]{\,\mathrm{#1}/\mathrm{#2}}
\newcommand{\mexp}[1]{\mathrm{e}^{#1}}
\newcommand{\nexp}[1]{\times 10^{#1}}

@@

\subsection[\label{S:M:Setup}]{Drive Beam Parameters}

In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
see from the self-modulated SPS beam in AWAKE. The baseline AWAKE drive beam contains $3\nexp{11}$ protons
\cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded in the
middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during self-modulation. The
needed gap between the two plasma cells also contributes to a decreased density of protons near the axis, and some of
the field is drained by other protons seeing an accelerating face within the drive beam. In total, the expected peak
$E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in the second cell
\cite{awake_collaboration:2016}. A single proton beam of $1.46\nexp{10}$, or $2.34\unit{nC}$ and $7\unit{kA}$, is needed
to drive an $E_{z}$ field of a comparable magnitude.

The single bunch approach was chosen to reduce simulation time for the 3D simulations, and to create a stable
environment for the witness beam. We are not considering the evolution of the proton beam in this test setup, so to
prevent the proton beam from evolving radially, we increased its mass.

The basline AWAKE drive beam current is insufficient to produce a plasma bubble. The plasma electrons are depleted to
around $65\%$ of nominal plasma density at the injection point of the electron beam. This condition is replicated in out
single bunch case. The single bunch setup also uses the baseline proton energy $W_{pb} = 400\unit{GeV}$.

\subsection[\label{S:M:Setup}]{Witness Beam Parameters}

The witness beam in our simulation differs from AWAKE baseline parameters on several key points. Initial beam energy is
set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This is to eliminate the problem of initial de-phasing of the witness
beam. AWAKE baseline witness beam energy for Run 1 is $W_{eb} = 10-20\unit{MeV}$ \cite{gschwendtner:2016}. Beam loading
of a short witness beam is sensitive to initial position. AWAKE Run 2 will likely require a higher initial energy, but a
$W_{eb} = 30--50\unit{MeV}$ is sufficient to minimise de-phasing \cite{berglyd_olsen:2015}. For this case we have
eliminated it entirely in order to reduce the number of variables in our parameter scans.

Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ causes the beam radius to rapidly shrink as the
beam enters the plasma \cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma
density. The relation is given by
\begin{align}
    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
\end{align}
where $\lambda_{p}$ is the plasma wavelength.

@@

%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
%~   unloaded wake)
The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
the electron witness beam sees consistent fields.
